Structural Divergence Analysis

### 2017-06-04 analysis-structure-core.Rmd
estructura-CN/WCN

@@

```{r correlation-da-CN} 
## CN core
CN = CN[indexes.core]

@@

>>>>

# calculate WCN

r.p.ref = matrix(ref.pdb$xyz[inds$xyz], nrow=3)
dist.r.p.ref = dist.xyz(t(r.p.ref))
WCN = c()
for (i in (1:ncol(r.p.ref))) {
  WCN[i] = sum(1/dist.r.p.ref[i, -i]^2)
}

@@

```{r correlation-da-CN} 
## CN core
CN = CN[indexes.core]
WCN = WCN[indexes.core]

@@

### Sequence - structure comparison

```{r structure-CN-comparison}

# compare profiles
## plot
par(pty = "s")

plot(x = d.exp$mean.z.RSD, y = log(CN), xlab = "<zRSDi> experimental")
plot(x = d.mut$mean.z.RSD, y = log(CN), xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = log(CN), xlab = "<zRSDi> selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN))
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN))
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN))

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN), method = "spearman")
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN), method = "spearman")
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN), method = "spearman")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")

# mean profiles

CN.simple = CN[!duplicated(CN)]

CN.i.mean = c()
exp.mean.z.RSD.i.mean = c()
mut.mean.z.RSD.i.mean = c()
medium.mean.z.RSD.i.mean = c()

count = 0
for (i in (CN.simple)) {
  count = count + 1
  index = 0
  for (j in (1:length(CN))){
    if (CN[j] == i) {
      index = cbind(index, j)
    } 
  }
  CN.i.mean[count] = mean(CN[index])
  exp.mean.z.RSD.i.mean[count] = mean(d.exp$mean.z.RSD[index])
  mut.mean.z.RSD.i.mean[count] = mean(d.mut$mean.z.RSD[index])
  medium.mean.z.RSD.i.mean[count] = mean(d.medium$mean.z.RSD[index])
}

## plot
par(pty = "s")

plot(x = exp.mean.z.RSD.i.mean, y = log(CN.i.mean), xlab = "mean <zRSDi> experimental for each CN", ylab = "log(CN)")
plot(x = mut.mean.z.RSD.i.mean, y = log(CN.i.mean), xlab = "mean <zRSDi> no-selection for each CN", ylab = "log(CN)")
plot(x = medium.mean.z.RSD.i.mean, y = log(CN.i.mean), xlab = "mean <zRSDi> selection for each CN", ylab = "log(CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(exp.mean.z.RSD.i.mean, log(CN.i.mean), method = "s")
r.mut.mean.z.RSD.CN = cor(mut.mean.z.RSD.i.mean, log(CN.i.mean), method = "s")
r.medium.mean.z.RSD.CN = cor(medium.mean.z.RSD.i.mean, log(CN.i.mean), method = "s")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(exp.mean.z.RSD.i.mean, log(CN.i.mean), method = "p")
r.mut.mean.z.RSD.CN = cor(mut.mean.z.RSD.i.mean, log(CN.i.mean), method = "p")
r.medium.mean.z.RSD.CN = cor(medium.mean.z.RSD.i.mean, log(CN.i.mean), method = "p")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
```

### Sequence - structure comparison WCN

```{r structure-WCN-comparison}

# compare profiles
## plot
par(pty = "s")

plot(x = d.exp$mean.z.RSD, y = log(WCN), xlab = "<zRSDi> experimental")
plot(x = d.mut$mean.z.RSD, y = log(WCN), xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = log(WCN), xlab = "<zRSDi> selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN))
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(WCN))
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(WCN))

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)", "<z.RSD> no-selection vs log(WCN)", "<z.RSD> selection vs log(WCN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (WCN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN), method = "spearman")
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(WCN), method = "spearman")
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(WCN), method = "spearman")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)", "<z.RSD> no-selection vs log(WCN)", "<z.RSD> selection vs log(WCN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (WCN)")

### 2017-06-04 analysis-structure-pfANM.Rmd
estructura-CN/WCN

ReadCA.fname <- "FUNCTIONS/ReadCA.R"
CalculateSideChainCM.fname <- "FUNCTIONS/CalculateSideChainCM.R"

# load functions
source(ReadCA.fname) 
source(CalculateSideChainCM.fname)
source(file.path(data.dir, "multiplot.R"))
source(file.path(data.dir, "my-functions.R"))
source("FUNCTIONS/readCA.R") 
```

@@

# read reference pdb and calculate resno, AA, and CN
reference.pdb.fname = file.path(data.dir,paste(reference, ".pdb", sep = ""))
ref.pdb = read.pdb(reference.pdb.fname)
inds = atom.select(ref.pdb, elety = "CA")
ref.pdb.ca = ref.pdb$atom[inds$atom,]
cmap.ca = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN = rowSums(cmap.ca, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!
n.sites = length(CN)
AA = ref.pdb.ca$resid
resno = ref.pdb.ca$resno
pdb.info = data.frame(resno, AA, CN)
names(pdb.info) = c("resno", "AA", paste("CN", as.character(R0), sep = ""))

if (data.dir == "OUT/out_subset_CM_ANM") {

  # Read PDB of p.ref
  pdb.ca = ReadCA(reference.pdb.fname, chain.p.ref)
  r.ca.p.ref = pdb.ca$xyz.calpha
  n.aa = pdb.ca$n.sites

  r.CM.p.ref = CalculateSideChainCM(reference.pdb.fname, chain.p.ref)
  n.CM = ncol(r.CM.p.ref)

  cmap.CM = cmap(r.CM.p.ref, dcut = R0, scut = 0, mask.lower = F)
  CN = rowSums(cmap.CM, na.rm = T) - 2
}

@@

# find the active site and its contacts
active.sites = d$site[d$shell == 0]
contacts.active.sites = d$site[d$shell == 1]

@@

```{r correlation-da-CN} 
## calculate correlations between profiles
r.min.da.CA.CN = cor(CN[-active.site.index], m.min.da.CM.CA$min.da.CA[-active.site.index])
r.min.da.CM.CN = cor(CN[-active.site.index], m.min.da.CM.CA$min.da.CM[-active.site.index])

cor.df = data.frame("comparison" = c("CN vs min.da.CA", "CN vs min.da.CM"), "R" = c(r.min.da.CA.CN, r.min.da.CM.CN))

knitr::kable(cor.df, digits = 2, caption = "Correlation between CN and the minimal distance to the active site")

## calculate correlations between profiles
r.sum.inv.da.CA.CN = cor(CN[-active.site.index], m.sum.inv.da.CM.CA$sum.inv.da.CA[-active.site.index])
r.sum.inv.da.CM.CN = cor(CN[-active.site.index], m.sum.inv.da.CM.CA$sum.inv.da.CM[-active.site.index])

cor.df = data.frame("comparison" = c("CN vs sum.inv.da.CA", "CN vs sum.inv.da.CM"), "R" = c(r.sum.inv.da.CA.CN, r.sum.inv.da.CM.CN))

knitr::kable(cor.df, digits = 2, caption = "Correlation between CN and the sum.inv distance to the active site")
```

@@

# correct indexes
if (data.dir == "OUT/out_subset_CM_ANM") {
  mut.site.mut = mut.site.mut - n.sites
  mut.site.medium.sel = mut.site.medium.sel - n.sites
  CN.CM = sim.data.mut$CN
  CN = c()

  for (i in (1:n.sites)) {
    CN[i] = CN.CM[which(mut.site.mut == i)][1]
  }
}

@@

plot(x = p.accept.mut, y = log(CN))
plot(x = p.accept.mut, y = score)
plot(x = score, y = log(CN))

## calculate corelations
r.p.accept.mut.CN = cor(p.accept.mut, log(CN))
r.p.accept.mut.score = cor(p.accept.mut, score)
r.score.CN = cor(score, log(CN))

cor.df = data.frame("comparison" = c("paccept no-selection vs log(CN)", "paccept no-selection vs score", "score vs log(CN)"),
                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))

@@

plot(x = p.accept.medium.sel, y = log(CN))
plot(x = p.accept.medium.sel, y = score)
plot(x = score, y = log(CN))

## calculate corelations
r.p.accept.medium.sel.CN = cor(p.accept.medium.sel, log(CN))
r.p.accept.medium.sel.score = cor(p.accept.medium.sel, score)
r.score.CN = cor(score, log(CN))

cor.df = data.frame("comparison" = c("paccept selection vs log(CN)", "paccept selection vs score", "score vs log(CN)"),
                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))

@@

```{r structure-CN-comparison}

plot(x = d.exp$mean.z.RSD, y = log(CN), xlab = "<zRSDi> experimental")
plot(x = d.mut$mean.z.RSD, y = log(CN), xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = log(CN), xlab = "<zRSDi> selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN))
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN))
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN))

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN), method = "spearman")
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN), method = "spearman")
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN), method = "spearman")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")

# mean profiles

CN.simple = CN[!duplicated(CN)]

CN.i.mean = c()
exp.mean.z.RSD.i.mean = c()
mut.mean.z.RSD.i.mean = c()
medium.mean.z.RSD.i.mean = c()

count = 0
for (i in (CN.simple)) {
  count = count + 1
  index = 0
  for (j in (1:length(CN))){
    if (CN[j] == i) {
      index = cbind(index, j)
    } 
  }
  CN.i.mean[count] = mean(CN[index])
  exp.mean.z.RSD.i.mean[count] = mean(d.exp$mean.z.RSD[index])
  mut.mean.z.RSD.i.mean[count] = mean(d.mut$mean.z.RSD[index])
  medium.mean.z.RSD.i.mean[count] = mean(d.medium$mean.z.RSD[index])
}

## plot
par(pty = "s")

plot(x = exp.mean.z.RSD.i.mean, y = log(CN.i.mean), xlab = "mean <zRSDi> experimental for each CN", ylab = "log(CN)")
plot(x = mut.mean.z.RSD.i.mean, y = log(CN.i.mean), xlab = "mean <zRSDi> no-selection for each CN", ylab = "log(CN)")
plot(x = medium.mean.z.RSD.i.mean, y = log(CN.i.mean), xlab = "mean <zRSDi> selection for each CN", ylab = "log(CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(exp.mean.z.RSD.i.mean, log(CN.i.mean), method = "s")
r.mut.mean.z.RSD.CN = cor(mut.mean.z.RSD.i.mean, log(CN.i.mean), method = "s")
r.medium.mean.z.RSD.CN = cor(medium.mean.z.RSD.i.mean, log(CN.i.mean), method = "s")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(exp.mean.z.RSD.i.mean, log(CN.i.mean), method = "p")
r.mut.mean.z.RSD.CN = cor(mut.mean.z.RSD.i.mean, log(CN.i.mean), method = "p")
r.medium.mean.z.RSD.CN = cor(medium.mean.z.RSD.i.mean, log(CN.i.mean), method = "p")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
```

### Sequence - structure comparison WCN

@@

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN))
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(WCN))
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(WCN))

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)", "<z.RSD> no-selection vs log(WCN)", "<z.RSD> selection vs log(WCN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

@@

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN), method = "spearman")
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(WCN), method = "spearman")
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(WCN), method = "spearman")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)", "<z.RSD> no-selection vs log(WCN)", "<z.RSD> selection vs log(WCN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

>>>>

# load functions
source(ReadCA.fname) 
source(CalculateSideChainCM.fname)
source(file.path(data.dir, "multiplot.R"))
source(file.path(data.dir, "my-functions.R"))
```

@@

# read reference pdb and calculate resno, AA, and CN
reference.pdb.fname = file.path(data.dir,paste(reference, ".pdb", sep = ""))
ref.pdb = read.pdb(reference.pdb.fname)
inds = atom.select(ref.pdb, elety = "CA")
ref.pdb.ca = ref.pdb$atom[inds$atom,]
n.sites = length(ref.pdb$xyz[inds$xyz])/3
AA = ref.pdb.ca$resid
resno = ref.pdb.ca$resno
pdb.info = data.frame(resno, AA)
names(pdb.info) = c("resno", "AA")

# calculate WCN
r.p.ref = matrix(ref.pdb$xyz[inds$xyz], nrow=3)
dist.r.p.ref = dist.xyz(t(r.p.ref))
WCN = c()
for (i in (1:ncol(r.p.ref))) {
  WCN[i] = sum(1/dist.r.p.ref[i, -i]^2)
}

@@

# find the active site and its contacts
active.sites = d$site[d$shell == 0]
contacts.active.sites = d$site[d$shell == 1]
```

@@

```{r correlation-da-WCN} 
## calculate correlations between profiles
r.min.da.CA.WCN = cor(WCN[-active.site.index], m.min.da.CM.CA$min.da.CA[-active.site.index])
r.min.da.CM.WCN = cor(WCN[-active.site.index], m.min.da.CM.CA$min.da.CM[-active.site.index])

cor.df = data.frame("comparison" = c("WCN vs min.da.CA", "WCN vs min.da.CM"), "R" = c(r.min.da.CA.WCN, r.min.da.CM.WCN))

knitr::kable(cor.df, digits = 2, caption = "Correlation between WCN and the minimal distance to the active site")

## calculate correlations between profiles
r.sum.inv.da.CA.WCN = cor(WCN[-active.site.index], m.sum.inv.da.CM.CA$sum.inv.da.CA[-active.site.index])
r.sum.inv.da.CM.WCN = cor(WCN[-active.site.index], m.sum.inv.da.CM.CA$sum.inv.da.CM[-active.site.index])

cor.df = data.frame("comparison" = c("WCN vs sum.inv.da.CA", "WCN vs sum.inv.da.CM"), "R" = c(r.sum.inv.da.CA.WCN, r.sum.inv.da.CM.WCN))

knitr::kable(cor.df, digits = 2, caption = "Correlation between WCN and the sum.inv distance to the active site")
```

@@

@@

plot(x = p.accept.mut, y = log(WCN))
plot(x = p.accept.mut, y = score)
plot(x = score, y = log(WCN))

## calculate corelations
r.p.accept.mut.WCN = cor(p.accept.mut, log(WCN))
r.p.accept.mut.score = cor(p.accept.mut, score)
r.score.WCN = cor(score, log(WCN))

cor.df = data.frame("comparison" = c("paccept no-selection vs log(WCN)", "paccept no-selection vs score", "score vs log(WCN)"),
                    "R" = c(r.p.accept.mut.WCN , r.p.accept.mut.score, r.score.WCN))

@@

plot(x = p.accept.medium.sel, y = log(WCN))
plot(x = p.accept.medium.sel, y = score)
plot(x = score, y = log(WCN))

## calculate corelations
r.p.accept.medium.sel.WCN = cor(p.accept.medium.sel, log(WCN))
r.p.accept.medium.sel.score = cor(p.accept.medium.sel, score)
r.score.WCN = cor(score, log(WCN))

cor.df = data.frame("comparison" = c("paccept selection vs log(WCN)", "paccept selection vs score", "score vs log(WCN)"),
                    "R" = c(r.p.accept.medium.sel.WCN , r.p.accept.medium.sel.score, r.score.WCN))

@@

@@

## calculate correlations
r.exp.mean.z.RSD.WCN = cor(d.exp$mean.z.RSD, log(WCN))
r.mut.mean.z.RSD.WCN = cor(d.mut$mean.z.RSD, log(WCN))
r.medium.mean.z.RSD.WCN = cor(d.medium$mean.z.RSD, log(WCN))

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)", "<z.RSD> no-selection vs log(WCN)", "<z.RSD> selection vs log(WCN)"),
                    "R" = c(r.exp.mean.z.RSD.WCN , r.mut.mean.z.RSD.WCN, r.medium.mean.z.RSD.WCN))

@@

## calculate correlations
r.exp.mean.z.RSD.WCN = cor(d.exp$mean.z.RSD, log(WCN), method = "spearman")
r.mut.mean.z.RSD.WCN = cor(d.mut$mean.z.RSD, log(WCN), method = "spearman")
r.medium.mean.z.RSD.WCN = cor(d.medium$mean.z.RSD, log(WCN), method = "spearman")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)", "<z.RSD> no-selection vs log(WCN)", "<z.RSD> selection vs log(WCN)"),
                    "R" = c(r.exp.mean.z.RSD.WCN , r.mut.mean.z.RSD.WCN, r.medium.mean.z.RSD.WCN))

### 2017-06-04 analysis-structure.Rmd
estructura-CN/WCN

knitr::kable(cor.df, digits = 2, caption = "Correlation structure (<z.RSD>) - sequence (CN)")
```

>>>>

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN), method = "spearman")
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN), method = "spearman")
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN), method = "spearman")

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
```
